### 2017-05-08 Hhh/Hhh.tex
First part of first round of corrections

\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
\label{chap:hhh}
In this chapter the search for a heavy Higgs boson decaying to a pair of $125\,\GeV$ Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of tau leptons, is discussed. In this analysis, which 
uses a dataset corresponding to $19.8\,\invfb$ collected during the 2012 p-p running
period of the \ac{LHC}, the \etau, \mutau and \tautau final states
of the di-tau pair are studied; these final states are referred to as channels. 
The results of this search are model-independent
upper limits on the heavy Higgs production cross section times branching ratio (\xsbr) into h(125)h(125)$\rightarrow \Pbottom\Pbottom\Pgt\Pgt$, for
which all three channels are combined. The \etau and \mutau channels will be described in this chapter. The \tautau channel will not
be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
In addition the results are interpreted in the context of the \ac{MSSM} and a type-II \ac{2HDM}.
These interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
For these results I contributed to the analysis of the \etau and \mutau channels,
and was responsible for limit setting for the \Htohh analysis. This included performing the model interpretations
of the \Htohh and \AtoZh analyses, plus their combination.
Both searches, and their interpretations, are detailed in reference \cite{CMS-HIG-14-034}.

The discovery of the $125\,\GeV$ Higgs boson by the ATLAS and CMS Collaborations in 2012 \cite{HDiscoveryATLAS,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the \ac{SM}. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios and some more
generic type-II \acp{2HDM}, a heavy neutral Higgs boson \PHiggs can decay to a pair of $125\,\GeV$ Higgs bosons for low values
of \tanb, probing a region of parameter space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low \tanb~region. The $\Pbottom\Pbottom\Pgt\Pgt$ final state is chosen for the combination
of the large $\PHiggslight(125) \rightarrow \Pbottom\Pbottom$ branching ratio and the cleaner $\PHiggslight(125) \rightarrow \Pgt\Pgt$ final state.

@@

In addition to the requirements on the di-tau pair, at least two jets with \pT~$>20\,\GeV$ are 
required. No b-tagging requirements are applied at this stage, these will be discussed 
in more detail in section \ref{sec:hhh_selection_categories}.

@@

This quantity is required to be smaller than $30\,\GeV$ in both channels. In events
where the missing energy and the light lepton are oriented back-to-back, \mT~is
large, whereas it is closer to zero when the two are aligned. In $\PW\rightarrow\ell\nu$
events, as the \PW boson is very heavy, the lepton and neutrino are more likely to be emitted back-to-back,
therefore \mT~will be large. For \Ztautau and \htotautau events, the neutrinos in the $\tau\rightarrow\ell\nu\nu$ decay 
 are more likely to travel in the same direction as the visible decay products of 
the tau, due to the smaller mass of the \Pgt compared with the \PW boson. Therefore requiring the
transverse mass to be less than $30\,\GeV$ reduces the \Wjets background. This effect
is also visible in figure \ref{fig:Hhh_selection_mt}, where the \Wjets and the much
smaller di-boson and single-top backgrounds are combined into the ``electroweak'' background contribution, drawn in red.
%In this analysis the presence of at least 2 jets increases the relative fraction of \ttbar 
%background events. Because the missing energy can now originate from multiple
%heavy objects (two tops) the missing transverse energy alignment is randomised. In some
%cases the lepton and missing transverse energy can be very much like the W decay
%topology, whereas in other cases \mT will be lower

After applying the \mT~selection, events are divided into three categories to maximise
sensitivity to the signal: 2jet-0tag (at least two jets, none of which are b-tagged), \mbox{2jet-1tag} 
(at least two jets, exactly one of which is b-tagged), \mbox{2jet-2tag} (at least two jets, at least two of which are b-tagged).
Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator.
The 2jet-0tag category does not collect much of the signal and is dominated by 
backgrounds, the 2jet-2tag category is the most sensitive to signal. 
Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the two-jet selection of the \mutau and \etau
channels, illustrates this.

\begin{figure}[h!]
\begin{center}
\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_mt_2012_log.pdf}}
\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_et_2012_log.pdf}}
\end{center}
\caption[Number of b-tagged jets in the two-jet selection of the \mutau and \etau channels.]{Number of b-tagged jets in the two-jet selection of the (a) \mutau and (b) \etau channels. The signal
at \mH~$=300\,\GeV$ and \tanb~$=2$ in the \ac{MSSM} low-\tanb~scenario, multiplied by a factor of 10, is overlaid.}
\label{fig:Hhh_selection_bjets}
\end{figure}

In signal events the di-tau pair and di-jet pair 
are the decay products of a $125\,\GeV$ Higgs boson, therefore their invariant
masses should be close to $125\,\GeV$. To reduce background contributions
from events where the di-tau or di-jet mass is not compatible with
$125\,\GeV$, requirements are made on $m_{jj}$, the di-jet invariant mass, and on $m_{\Pgt\Pgt}$, the di-tau
invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
a likelihood-based estimate of the di-tau mass using the visible decay products
of the taus and the reconstructed \MET. The use of this algorithm greatly
improves the separation between $\PZ\rightarrow\Pgt\Pgt$ and $\PHiggs\rightarrow\Pgt\Pgt$ events, 
which is of great importance for the \ac{SM} $\PHiggs\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
By requiring $70 < m_{jj} < 150\,\GeV$ and $90 < m_{\Pgt\Pgt} < 150\,\GeV$ a 
large number of background events can be rejected, while retaining
most of the signal. This is illustrated in figure \ref{fig:Hhh_selection_masscuts} for 
the 2jet-2tag category.

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\Pgt\Pgt}$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_mt_2012.pdf}}
\subfloat[$m_{jj}$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_mt_2012.pdf}}
\end{center}
\caption[Reconstructed di-tau invariant mass and di-jet invariant mass in
the \mbox{2jet-2tag} category of the \mutau channel.]{(a) Reconstructed di-tau invariant mass and (b) di-jet invariant mass in the \mbox{2jet-2tag} category of the \mutau
channel. The signal for a heavy Higgs boson \PHiggs with mass \mH~$= 300\,\GeV$ at \tanb~$=2$ in the low-\tanb~MSSM scenario, multiplied by a factor 10, is overlaid.
The signal peaks at around $125\,\GeV$ in both variables.}
\label{fig:Hhh_selection_masscuts}
\end{figure}

\section{\acl{MC} simulation to data correction factors}
\label{sec:hhh_datamc}
Simulated samples are used for the estimation of some of the backgrounds and the signal, 
and it is therefore important to correct for any mis-modelling. The \ac{MC} simulation to data 
correction factors used for this are estimated in dedicated control regions.

@@

To correct for the differences in b-tagging efficiency and light jet mis-tagging
rates between data and simulation, \pT~and $\eta$~dependent scale factors are 
derived using the method described in reference \cite{BTV8TeV}. There are separate scale factors for 
b-/c-jets and light jets. In this analysis the ``promote-demote'' method
is used to apply these.

In this method a demotion or promotion probability is assigned to every
jet as:
\begin{align}\label{eqn:promotedemote}
P(\text{demote}) &= 1 - \text{SF} \text{  for SF < 1 }  \notag \\
P(\text{promote}) &= \frac{(\text{SF} - 1)(\epsilon_{\text{MC}}-1)}{\text{SF}} \text{    for SF > 1},
\end{align}
Where SF is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b-tagging efficiency in simulated events for the type of jet (light, b- or c-)
under consideration.

@@

In a kinematic fit constraints are made on the event kinematics, in the
case of this analysis these constraints are
$m(\Pgt_{1},\Pgt_{2}) = m_{\PHiggslight} = 125\,\GeV$  and
$m(\Pbottom_{1},\Pbottom_{2}) = m_{\PHiggslight} = 125\,\GeV$.
The kinematic observables related to the hadronic taus and jets
are varied within their uncertainties to fulfil these 
constraints. A $\chi^2$ cost term is introduced for each
observable that is varied with respect to the measurement,
the aim of the fit is to minimise the sum of these $\chi^2$ terms.

For b-jets, the reconstructed direction in $\eta$ and $\phi$ is 
assumed to be measured accurately in comparison with their energy.
Therefore only their energy is varied in the fit. In addition, we assume
that uncertainties in the energy measurement directly translate to
uncertainties in the momentum measurement, therefore $\vec{\beta} = \vec{p}/E$ is
also kept constant.

@@

The measured recoil is 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilmeas}
\vec{p_{\text{T,recoil}}}^{\text{meas}} = -\vec{p_{\text{T,\PHiggs}}}^{\text{meas}} = -\vec{p_{\text{T,miss}}}^{\text{meas}} - \vec{p_{\text{T},\Pbottom 1}}^{\text{meas}} - \vec{p_{\text{T},\Pbottom 2}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{\text{meas}},
\end{equation}
and the recoil from the fit is,
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilfit}
\vec{p_{\text{T,recoil}}}^{\text{fit}} = -\vec{p_{\text{T,\PHiggs}}}^{\text{fit}} = - \vec{p_{\text{T},\Pbottom 1}}^{\text{fit}} - \vec{p_{\text{T},\Pbottom 2}}^{\text{fit}} - \vec{p_{\text{T},\Pgt_1}}^{\text{fit}} - \vec{p_{\text{T},\Pgt_2}}^{\text{fit}}.
\end{equation}
A $\chi^2$ corresponding to the agreement between the fitted and measured recoil is reconstructed as
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilchi2}
\chi^2_{\text{recoil}} = (\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{meas}})^T V_{\text{recoil}}^{-1}(\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{meas}}),
\end{equation}
where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as 
\begin{equation}\label{eqn:kinfit_recoilcov}
V_{\text{recoil}} = V_{\vec{p_{\text{T,miss}}}} - V_{\Pbottom {1}} - V_{\Pbottom 2},
\end{equation}
 from the covariance matrices of the b-jets and
the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET,
while the covariance matrices of the b-jets can be written in terms of the position, momentum and resolution of the b-jets. 
The total $\chi^2$ term that needs to be minimised in the fit can then be written as
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_chitot}
\chi^2 = \chi^2_{\Pbottom 1} + \chi^2_{\Pbottom 2} + \chi^2_{\text{recoil}}.
\end{equation}
The results of the kinematic fit are the tau and b-jet four-vectors with their energies and momenta
set to the best fit values found for them in the fit. These can then be added together to find
the mass of the heavy Higgs boson as reconstructed by the kinematic fit.

@@

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data-driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category the total
yield after the initial event selection, before subdividing into categories, as
estimated in the simulated \Ztautau sample is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from the \ttbar background in the embedded
sample is evaluated using the dedicated \ttbar embedded sample. This contribution
is subtracted from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using simulation.
These are checked against data in dedicated control regions. One such control
region uses the \emu final state of the di-tau pair. A correction factor is estimated in 
this control region and applied to the yield estimate from simulation in the signal region. 
%The resulting scale factor is 1.033 ± 0.013(stat.) ± 0.088(syst.). 
\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT~to
be less than $30\,\GeV$. To estimate the remaining contribution
in the signal region a sideband with \mT~greater
than $70\,\GeV$ is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high-\mT~to \mbox{low-\mT}~extrapolation
 factor is determined from the \Wjets simulation.
The yield in the signal region is given by the data yield in the high-\mT~sideband, with
other backgrounds subtracted, multiplied by this extrapolation factor.
In the 2jet-2tag category, a slightly different high-\mT~sideband of $60$--$120\,\GeV$ is used 
as above $120\,\GeV$ the \ttbar background dominates over \Wjets. 
The method of extrapolating this yield estimate into
the signal region is otherwise analogous.

@@

The first term in equation \ref{eqn:hhh_likelihood} runs over all bins of the $m_{\PHiggs}^{\text{kinfit}}$ distribution 
in all channels and categories. The parameter $s$ represents the number of expected signal events
in each bin, and $b$ the number of expected background events. These are functions of 
$\theta$, the full set of nuisance parameters. The signal strength
modifier $\mu$ can represent different quantities depending on the normalisation of the 
signal expectation. In the case of the \Htohhtobbtautau analysis the signal is normalised
to $1\,\picobarn$, so the signal strength modifier represents
the \xsbr of a possible signal.

The second term in equation \ref{eqn:hhh_likelihood}, $p(\tilde{\theta}|\theta)$ represents the full set of 
probability density functions of the uncertainties on the nominal
values of the nuisance parameters $\tilde{\theta}$. Each nuisance parameter represents a systematic uncertainty
as discussed in section~\ref{sec:hhh_uncs}. The functional form of the probability density function
depends on the type of systematic uncertainty. Normalisation uncertainties are applied with log-normal constraints, which
ensures that the process yields can never become negative, and therefore unphysical, in the fit. 
%For a log-normal constraint an $n~\sigma$ upwards pull on a nuisance parameter $\theta$ measured with a systematic
%uncertainty $\kappa$ multiplies the yield of processes affected by this nuisance parameter by $(1+\kappa)^n$, while
%an $n~\sigma$ downwards pull multiplies the process yields by $(1+\kappa)^{-n}$, ensuring that process
%yields do not become negative. 
Shape uncertainties are accounted for using a vertical template morphing
technique~\cite{temp-morph-2011}. For each nuisance parameter that affects the shape of the fitted distribution, two additional
templates corresponding to the quantity varied by $\pm 1 \sigma$ are generated. A nuisance
parameter is added to the likelihood model with a gaussian constraint to smoothly interpolate between
the nominal and $\pm 1\sigma$ templates. Limitations in the number of events used to construct the shape templates
are accounted for by the Barlow-Beeston method\cite{BarlowBeeston}, in which each of the bins of each 
shape template is allowed to vary within its statistical uncertainty, independent of the other bins. %These
%variations are controlled by log-normal constraints in the likelihood function.

@@

and 
\begin{equation}\label{eqn:hhh_pvaluebkg}
1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \int_{q_{0}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} ,
\end{equation}

>>>>

\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
\label{chap:hhh}
The discovery of the $125\,\GeV$ Higgs boson by the ATLAS and CMS Collaborations in 2012 \cite{HDiscoveryATLAS,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the \ac{SM}. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios and some more
generic type-II \acp{2HDM}, a heavy neutral Higgs boson \PHiggs can decay to a pair of $125\,\GeV$ Higgs bosons for low values
of \tanb, probing a region of parameter space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low \tanb~region. The $\Pbottom\Pbottom\Pgt\Pgt$ final state is chosen for the combination
of the large $\PHiggslight(125) \rightarrow \Pbottom\Pbottom$ branching ratio and the cleaner $\PHiggslight(125) \rightarrow \Pgt\Pgt$ final state.

In this chapter the search for a heavy Higgs boson decaying to a pair of $125\,\GeV$ Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of tau leptons, is discussed. In this analysis, which 
uses a dataset corresponding to $19.8\,\invfb$ collected during the 2012 p-p running
period of the \ac{LHC}, the \etau, \mutau and \tautau final states
of the di-tau pair are studied; these final states are referred to as channels. 
The results of this search are model-independent
upper limits on the heavy Higgs production cross section times branching ratio (\xsbr) into h(125)h(125)$\rightarrow \Pbottom\Pbottom\Pgt\Pgt$, for
which all three channels are combined. The \etau and \mutau channels will be described in this chapter. The \tautau channel will not
be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
In addition the results are interpreted in the context of the \ac{MSSM} and a type-II \ac{2HDM}.
These interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
For these results I contributed to the analysis of the \etau and \mutau channels,
and was responsible for limit setting for the \Htohh analysis. This included performing the model interpretations
of the \Htohh and \AtoZh analyses, plus their combination.
Both searches, and their interpretations, are detailed in reference \cite{CMS-HIG-14-034}.

@@

In addition to the requirements on the di-tau pair, at least two jets with \pT~$>20\,\GeV$ are 
required. No b-tagging requirements are applied at this stage; these will be discussed 
in more detail in section \ref{sec:hhh_selection_categories}.

@@

This quantity is required to be smaller than $30\,\GeV$ in both channels. In events
where the missing energy and the light lepton are oriented back-to-back, \mT~is
large, whereas it is closer to zero when the two are aligned. In $\PW\rightarrow\ell\nu$
events, as the \PW boson is very heavy, the lepton and neutrino are more likely to be emitted back-to-back, and
therefore \mT~will be large. For \Ztautau and \htotautau events, the neutrinos in the $\tau\rightarrow\ell\nu\nu$ decay 
 are more likely to travel in the same direction as the visible decay products of 
the tau, due to the smaller mass of the \Pgt compared with the \PW boson. Therefore requiring the
transverse mass to be less than $30\,\GeV$ reduces the \Wjets background. This effect
is also visible in figure \ref{fig:Hhh_selection_mt}, where the \Wjets and the much
smaller di-boson and single-top backgrounds are combined into the ``electroweak'' background contribution, drawn in red.
%In this analysis the presence of at least 2 jets increases the relative fraction of \ttbar 
%background events. Because the missing energy can now originate from multiple
%heavy objects (two tops) the missing transverse energy alignment is randomised. In some
%cases the lepton and missing transverse energy can be very much like the W decay
%topology, whereas in other cases \mT will be lower

After applying the \mT~selection, events are divided into three categories to maximise
sensitivity to the signal: 2jet-0tag (at least two jets, none of which are b-tagged), \mbox{2jet-1tag} 
(at least two jets, exactly one of which is b-tagged), \mbox{2jet-2tag} (at least two jets, at least two of which are b-tagged).
Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator.
The 2jet-0tag category does not collect much of the signal and is dominated by 
backgrounds, and the 2jet-2tag category is the most sensitive to signal. 
Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the two-jet selection of the \mutau and \etau
channels, illustrates this.

\begin{figure}[h!]
\begin{center}
\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_mt_2012_log_corrs.pdf}}
\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_et_2012_log_corrs.pdf}}
\end{center}
\caption[Number of b-tagged jets in the two-jet selection of the \mutau and \etau channels.]{Number of b-tagged jets in the two-jet selection of the (a) \mutau and (b) \etau channels. The signal
at \mH~$=300\,\GeV$ and \tanb~$=2$ in the \ac{MSSM} low-\tanb~scenario, multiplied by a factor of 10, is overlaid.}
\label{fig:Hhh_selection_bjets}
\end{figure}

In signal events the di-tau pair and di-jet pair 
are the decay products of a $125\,\GeV$ Higgs boson, and therefore their invariant
masses should be close to $125\,\GeV$. To reduce background contributions
from events where the di-tau or di-jet mass is not compatible with
$125\,\GeV$, requirements are made on $m_{jj}$, the di-jet invariant mass, and on $m_{\Pgt\Pgt}$, the di-tau
invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
a likelihood-based estimate of the di-tau mass using the visible decay products
of the taus and the reconstructed \MET. The use of this algorithm greatly
improves the separation between $\PZ\rightarrow\Pgt\Pgt$ and $\PHiggs\rightarrow\Pgt\Pgt$ events, 
which is of great importance for the \ac{SM} $\PHiggs\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
By requiring $70 < m_{jj} < 150\,\GeV$ and $90 < m_{\Pgt\Pgt} < 150\,\GeV$, a 
large number of background events can be rejected, while retaining
most of the signal. This is illustrated in figure \ref{fig:Hhh_selection_masscuts} for 
the 2jet-2tag category.

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\Pgt\Pgt}$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_mt_2012_corrs.pdf}}
\subfloat[$m_{jj}$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_mt_2012_corrs.pdf}}
\end{center}
\caption[Reconstructed di-tau invariant mass and di-jet invariant mass in
the \mbox{2jet-2tag} category of the \mutau channel.]{(a) Reconstructed di-tau invariant mass and (b) di-jet invariant mass in the \mbox{2jet-2tag} category of the \mutau
channel. The signal for a heavy Higgs boson \PHiggs with mass \mH~$= 300\,\GeV$ at \tanb~$=2$ in the low-\tanb~MSSM scenario, multiplied by a factor 10, is overlaid.
The signal peaks at around $125\,\GeV$ in both variables.}
\label{fig:Hhh_selection_masscuts}
\end{figure}

\section{\acl{MC} simulation-to-data correction factors}
\label{sec:hhh_datamc}
Simulated samples are used for the estimation of some of the backgrounds and the signal, 
and it is therefore important to correct for any mis-modelling. The \ac{MC} simulation-to-data 
correction factors used for this are estimated in dedicated control regions.

@@

To correct for the differences in b-tagging efficiency and light jet mis-tagging
rates between data and simulation, \pT-and $\eta$-dependent scale factors are 
derived using the method described in reference \cite{BTV8TeV}. There are separate scale factors for 
b-/c-jets and light jets.

In this analysis the ``promote-demote'' method
is used to apply these scale factors. In this method a demotion 
or promotion probability is assigned to every
jet as:
\begin{align}\label{eqn:promotedemote}
P(\text{demote}) &= 1 - \text{SF} \text{  for SF < 1 }  \notag \\
P(\text{promote}) &= \frac{(\text{SF} - 1)(\epsilon_{\text{MC}}-1)}{\text{SF}} \text{    for SF > 1},
\end{align}
where `SF' is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b-tagging efficiency in simulated events for the type of jet (light, b- or c-)
under consideration.

@@

In a kinematic fit constraints are made on the event kinematics, in the
case of this analysis these constraints are
$m(\Pgt_{1},\Pgt_{2}) = m_{\PHiggslight} = 125\,\GeV$  and
$m(\Pbottom_{1},\Pbottom_{2}) = m_{\PHiggslight} = 125\,\GeV$.
The kinematic observables related to the hadronic taus and jets
are varied within their uncertainties to fulfil these 
constraints. A $\chi^2$ cost term is introduced for each
observable that is varied with respect to the measurement;
the aim of the fit is to minimise the sum of these $\chi^2$ terms.

For b-jets, the reconstructed direction in $\eta$ and $\phi$ is 
assumed to be measured accurately in comparison with their energy.
Therefore only their energy is varied in the fit. In addition, we assume
that uncertainties in the energy measurement directly translate to
uncertainties in the momentum measurement, and therefore $\vec{\beta} = \vec{p}/E$ is
also kept constant.

@@

The measured recoil is 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilmeas}
\vec{p}_{\text{T,recoil}}^{\text{ meas}} = -\vec{p}_{\text{T,\PHiggs}}^{\text{ meas}} = -\vec{p}_{\text{T,miss}}^{\text{ meas}} - \vec{p}_{\text{T},\Pbottom 1}^{\text{ meas}} - \vec{p}_{\text{T},\Pbottom 2}^{\text{ meas}} - \vec{p}_{\text{T},\Pgt_1^{\text{vis}}}^{\text{ meas}} - \vec{p}_{\text{T},\Pgt_2^{\text{vis}}}^{\text{ meas}},
\end{equation}
and the recoil from the fit is,
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilfit}
\vec{p}_{\text{T,recoil}}^{\text{ fit}} = -\vec{p}_{\text{T,\PHiggs}}^{\text{ fit}} = - \vec{p}_{\text{T},\Pbottom 1}^{\text{ fit}} - \vec{p}_{\text{T},\Pbottom 2}^{\text{ fit}} - \vec{p}_{\text{T},\Pgt_1}^{\text{ fit}} - \vec{p}_{\text{T},\Pgt_2}^{\text{ fit}}.
\end{equation}
A $\chi^2$ corresponding to the agreement between the fitted and measured recoil is reconstructed as
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilchi2}
\chi^2_{\text{recoil}} = (\vec{p}_{\text{T,recoil}}^{\text{ fit}} - \vec{p}_{\text{T,recoil}}^{\text{ meas}})^T V_{\text{recoil}}^{-1}(\vec{p}_{\text{T,recoil}}^{\text{ fit}} - \vec{p}_{\text{T,recoil}}^{\text{ meas}}),
\end{equation}
where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as 
\begin{equation}\label{eqn:kinfit_recoilcov}
V_{\text{recoil}} = V_{\vec{p}_{\text{T,miss}}} - V_{\Pbottom {1}} - V_{\Pbottom 2},
\end{equation}
 from the covariance matrices of the b-jets and
the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET,
while the covariance matrices of the b-jets can be written in terms of the position, momentum and resolution of the b-jets. 
The total $\chi^2$ term that needs to be minimised in the fit can then be written as
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_chitot}
\chi^2 = \chi^2_{\Pbottom 1} + \chi^2_{\Pbottom 2} + \chi^2_{\text{recoil}}.
\end{equation}
The results of the kinematic fit are the tau and b-jet four-vectors with their energies and momenta
set to the best fit values found for them in the fit. These can then be added together to find
the mass of the heavy Higgs boson as reconstructed by the kinematic fit.

@@

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data-driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. The yield of
\Ztautau in each category is evaluated in two steps. In the first
step the total yield after the initial event selection, before subdividing into categories,
is evaluated in the simulated \Ztautau sample. In the second step the yield obtained 
in the first step is scaled by the efficiency with which such events pass the 
category selection in the embedded sample.
The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from the \ttbar background in the embedded
sample is evaluated using the dedicated \ttbar embedded sample. This contribution
is subtracted from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using simulation.
These are checked against data in dedicated control regions. One such control
region uses the \emu final state of the di-tau pair. A correction factor is estimated in 
this control region and applied to the yield estimate from simulation in the signal region. 
%The resulting scale factor is 1.033 ± 0.013(stat.) ± 0.088(syst.). 
\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT~to
be less than $30\,\GeV$. To estimate the remaining contribution
in the signal region a sideband with \mT~greater
than $70\,\GeV$ is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high-\mT~to \mbox{low-\mT}~extrapolation
 factor is determined from the \Wjets simulation.
The yield in the signal region is given by the data yield in the high-\mT~sideband, with
other backgrounds subtracted, multiplied by this extrapolation factor.
In the 2jet-2tag category, a slightly different high-\mT~sideband of $60$--$120\,\GeV$ is used 
as above $120\,\GeV$ the \ttbar background dominates over \Wjets. 
The method of extrapolating this yield estimate into
the signal region is otherwise analogous.

@@

The first factor in equation \ref{eqn:hhh_likelihood} runs over all bins of the $m_{\PHiggs}^{\text{kinfit}}$ distribution 
in all channels and categories. The parameter $s$ represents the number of expected signal events
in each bin, and $b$ the number of expected background events. These are functions of 
$\theta$, the full set of nuisance parameters. The signal strength
modifier $\mu$ can represent different quantities depending on the normalisation of the 
signal expectation. In the case of the \Htohhtobbtautau analysis the signal is normalised
to $1\,\picobarn$, so the signal strength modifier represents
the \xsbr of a possible signal.

The second factor in equation \ref{eqn:hhh_likelihood}, $p(\tilde{\theta}|\theta)$ represents the full set of 
probability density functions of the uncertainties on the nominal
values of the nuisance parameters $\tilde{\theta}$. Each nuisance parameter represents a systematic uncertainty
as discussed in section~\ref{sec:hhh_uncs}. The functional form of the probability density function
depends on the type of systematic uncertainty. Normalisation uncertainties are applied with log-normal constraints, which
ensures that the process yields can never become negative, and therefore unphysical, in the fit. 
%For a log-normal constraint an $n~\sigma$ upwards pull on a nuisance parameter $\theta$ measured with a systematic
%uncertainty $\kappa$ multiplies the yield of processes affected by this nuisance parameter by $(1+\kappa)^n$, while
%an $n~\sigma$ downwards pull multiplies the process yields by $(1+\kappa)^{-n}$, ensuring that process
%yields do not become negative. 
Shape uncertainties are accounted for using a vertical template morphing
technique~\cite{temp-morph-2011}. For each nuisance parameter that affects the shape of the fitted distribution, two additional
templates corresponding to the quantity varied by $\pm 1 \sigma$ are generated. A nuisance
parameter is added to the likelihood model with a gaussian constraint to smoothly interpolate between
the nominal and $\pm 1\sigma$ templates. Limitations in the number of events used to construct the shape templates
are accounted for by the Barlow-Beeston method\cite{BarlowBeeston}, in which each of the bins of each 
shape template is allowed to vary within its statistical uncertainty, independent of the other bins. %These
%variations are controlled by log-normal constraints in the likelihood function.

@@

and 
\begin{equation}\label{eqn:hhh_pvaluebkg}
1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \int_{q_{\mu}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} ,
\end{equation}
